Finite Property Convex Elicitation Notes

### 2018-09-14 jessie-writeup/proofs.tex
Small tweaks to Jessie's writeup

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}

@@

We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \to \Gamma(p) \cap \R'$.

\begin{definition}
  Consider two labeled properties $\Gamma'$ and $\Gamma$.
  We say $\Gamma' < \Gamma : \Delta(\Y) \to \R$ if you get $\Gamma'$ by removing reports from $\Gamma$.
  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subset \R$)
\end{definition}

@@

\begin{lemma}\label{conj:closed-level-sets}
  For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
  i.e. $\Gamma_r = \text{cl} (\Gamma_r)$.
\end{lemma}
\begin{proof}
  \emph{Sketch:  } Since property values are the subgradient sets of the overarching Scoring Rule and subgradient sets are closed, the level sets of $\Gamma$ are closed.
\end{proof}

@@

Notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\P = \Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?)
\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: x > 0,  \forall q \in B(x,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\P$). \jessie{I think...}
\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:intersect-lev-sets}
  Let the property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
  Consider $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
  Then for every $r \in \R$, there exist a finite set $R \in 2^{\R'}$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
\end{conjecture}

@@

\begin{proof}
\jessie{To show:  For any nonredundant, nondegenerate $\Gamma' < \Gamma$, that $\strip(\Gamma') = \strip(\Gamma)$}.

Consider the nonredundant, nondegenerate properties $\Gamma' < \Gamma$.
As $\strip$ is well-defined, clearly $\strip(\Gamma) = \Theta$ is a well-defined set of level sets.

We can define them as $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$ and similarly $\tilde \Gamma = \Gamma \cap \tilde \R$ for $\tilde \R \subseteq \R$.
Then we can write $\Theta' := \strip(\Gamma') = \{\Gamma_r : r \in \R' \}$ and $\Theta := \strip(\tilde \Gamma) = \{ \Gamma_{\tilde r} : \tilde r \in \tilde \R \}$.

Consider $\theta \in \Theta$.
Then there is some $r \in \R$ such that $r\in\Gamma(p)\cap \R \implies r \in \Gamma(p)$ for all $p \in \theta$.
(Note:  If $r \in \R'$, then, trivially, $r \in \Gamma(p) \cap \R'$ for all $p \in \theta$.)
If $r \not \in \R'$, then as $\Gamma'$ is nondegenerate, there exists some $r' \in \R'$ so that $r' \in \Gamma'(p) = \Gamma(p) \cap \R'$ for all $p \in \theta$.
Therefore, $\theta \in \Theta'$,
Since $\theta \in \Theta \implies \theta \in \Theta'$, we know $\Theta \subseteq \Theta'$.

As $\R' \subseteq \R$, it is easy to see  $\Theta' \subseteq \Theta$, and therefore $\Theta = \Theta'$.

@@

Let us consider some $r\in\R \setminus \R'$.
The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
By Conjecture \ref{conj:intersect-lev-sets}, there exist a set of finite reports $R \in 2^{\R'}$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
As there are only finitely many combinations of reports $R$ in the finite set $\R'$, then the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \in 2^{\R'} \}$ is finite.

@@

For contradiction, suppose there was some $s \in \R$ such that $\E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.
%\jessie{(Note that if $E_p L(s,Y) < \E_p L(r_\theta, Y)$, then $r_\theta \not\in \Gamma(p)$, so we reduce to an equality.)}

As $p \in \inter{\theta}$, we then know $\E_q L(r_\theta, Y) \leq \E_q L(s,Y)$ for all $q \in B(\epsilon, p)$.
Therefore, $\Gamma_s \subseteq \inter{\Gamma_{r_\theta}} \subseteq \Gamma_{r_\theta}$.
As there are no dominated reports (by non-redundancy of $\Gamma$), this implies $\Gamma_s = \Gamma_{r_\theta}$.
Therefore, we can see that $r_\theta = s$, since otherwise we would contradict nonredundancy of $\Gamma$.
As $r_\theta = s$, we can then say $r_\theta$ is the unique property value on $\inter{\theta}$.
Therefore, $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{conjecture}{Conjecture}
\newtheorem{notation}{Notation}

@@

\begin{notation}
We will use the following notation: $\Gamma' = \Gamma \cap \R'$ is the property $\Gamma' : p \to \Gamma(p) \cap \R'$.  
\end{notation}

\begin{notation}
  Consider two labeled properties $\Gamma'$ and $\Gamma$.
  We say $\Gamma' < \Gamma : \Delta(\Y) \to \R$ if you get $\Gamma'$ by removing reports from $\Gamma$.
  (i.e. $\Gamma' = \R' \cap \Gamma$ for some $\R' \subset \R$)
\end{notation}

@@

\begin{lemma}\label{conj:closed-level-sets}
  For any $r\in\R$, the level set $\Gamma_r = \{ p \in \Delta(\Y) : \Gamma(p) = r \}$ is closed.
\end{lemma}
\begin{proof}
  \emph{Sketch:  } Since property values are the subgradient sets of the overarching Scoring Rule and subgradient sets are closed, the level sets of $\Gamma$ are closed.
\end{proof}

@@

Notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item The interior of a level set $X$ is defined as $\inter{X} = \{p \in X: \epsilon > 0,  \forall q \in B(\epsilon,p), \argmin_rE_p L(r,Y) = \argmin_r E_q L(r,Y)\}$
\item A level set is \emph{full-dimensional} if dim(affine hull($\Gamma_r$)) is equal to dim($\Delta(\Y)$). 
\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:intersect-lev-sets}
  Let the property $\Gamma$ have a finite set $\Theta$ of full-dimensional level sets, so that for all $\theta \in \Theta$,  there is a unique optimal report $r_\theta$ for all $p \in \inter{\theta}$.
  Consider $\R' := \{ r_\theta\}_{\theta \in \Theta}$.
  Then for every $r \in \R$, there exists a finite set $R \in 2^{\R'}$ so that $\Gamma_r = \bigcap_{r' \in R} \Gamma_{r'}$.
\end{conjecture}

@@

\begin{proof}
\jessie{To show:  For any nonredundant, nondegenerate $\Gamma' < \Gamma$, that $\strip(\Gamma') = \strip(\Gamma) = \Theta$}.

Consider the nonredundant, nondegenerate properties $\Gamma' < \Gamma$.
As $\strip$ is well-defined, clearly $\Theta := \strip(\Gamma)$ is a well-defined set of level sets (read: property).

We can define a nondegenerate $\Gamma' = \Gamma \cap \R'$ for some $\R' \subseteq \R$.
Then we can write $\Theta' := \strip(\Gamma') = \{\Gamma_r : r \in \R' \}$.

Our hope is to show $\Theta = \Theta'$.

As $\R' \subseteq \R$, it is easy to see  $\Theta' \subseteq \Theta$, and therefore it is just left to show $\Theta \subseteq \Theta'$.

Consider $\theta \in \Theta$.
Then there is some $r \in \R$ such that $r\in\Gamma(p)\cap \R \implies r \in \Gamma(p)$ for all $p \in \theta$.

We now want to show that there is some $r' \in \R'$ such that $r' \in \Gamma(p) \forall p \in \theta$.
As $\Gamma'$ is nondegenerate, there exists some $r' \in \R'$ so that $r' \in \Gamma'(p) = \Gamma(p) \cap \R'$ for all $p \in \theta$.
Therefore, $\theta \in \Theta'$,
Since $\theta \in \Theta \implies \theta \in \Theta'$, we know $\Theta \subseteq \Theta'$.

As $\Theta' \subseteq \Theta$, we conclude $\Theta = \Theta'$.

@@

Let us consider some $r\in\R \setminus \R'$.
The level set $\Gamma_r = \{p : \Gamma(p) = r\}$ by definition.
As $r \not\in \R'$, the interior is empty; that is, $\inter{\Gamma_r} = \emptyset$.
% For any $p \in \Gamma_r$, then, there is some $q \in B(\epsilon, p)$ such that $\E_q L(r', Y) < \E_q L(r,y)$ for some $r' \in \R'$.
% As $r = \argmin_{\tilde{r}} \E_p L(\tilde{r}, Y)$, then we observe $\E_p L(r, Y) = \E_p L(r', Y) = \min_{\tilde{r}}\E_p L(\tilde{r}, Y)$ for $p \in \Gamma_r$. 
% Thus, $\Gamma_r \subseteq \Gamma_{r'}$.
By Conjecture \ref{conj:intersect-lev-sets}, there exist a set of finite reports $R \in 2^{\R'}$ such that $\bigcap_{r'\in R} \Gamma_{r'} = \Gamma_r$.
As the set $\R'$ is finite, then the power set $2^{\R'}$ is finite. t
Thus, the set $\{ \Gamma_r : r \in \R \setminus \R' \} =  \{ \bigcap_{r_1 \in R} \Gamma_{r_1} : R \in 2^{\R'} \}$ is finite.

@@

For contradiction, suppose there was some $s \in \R$ such that $\E_p L(s,Y) = \E_p L(r_\theta, Y)$ for some $p \in \inter{\theta}$.

As $p \in \inter{\theta}$, we then know $\E_q L(r_\theta, Y) \leq \E_q L(s,Y)$ for all $q \in B(\epsilon, p)$.
Therefore, $\Gamma_s \subseteq \inter{\Gamma_{r_\theta}} \subseteq \Gamma_{r_\theta}$.
As there are no dominated reports (by non-redundancy of $\Gamma$), this implies $\Gamma_s = \Gamma_{r_\theta}$.
Therefore, we can see that $r_\theta = s$, since otherwise we would contradict non-redundancy of $\Gamma$.
As $r_\theta = s$, we can then say $r_\theta$ is the unique property value on $\inter{\theta}$.
Therefore, $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
